Article 1 : Pathway found for treatment-resistant lung cancer

### 2019-10-21 _posts/2019-09-18-article-1/article-1.Rmd
test pour le mettre en ligne
suppression de l'article dans le texte

---
title: "Article 1 : "
author:
  - name: Aurélie Pinchart
date: 09-18-2019
categories:
  - 
  - 
preview: 
output:
  distill::distill_article:
    self_contained: false
---

@@

![]

@@

|                              |                                                                     |
| ---------------------------- | ------------------------------------------------------------------- |
| Researchers                  | (insert names and, if possible, professions)                        |
| Published in?                | (insert date)                                                       |
| General topic?               |  (summarize the topic in one or two sentences)                      |
| Procedure/what was examined? | (Give some details about the topic, i.e. methodology/material/etc.) |
| Conclusions/discovery?       |  (what did the researchers conclude? Did they find something?)      |
| Remaining questions?         | (check if there are still interrogations at the end of the article) |

>>>>

---
title: "Article 1 : Pathway found for treatment-resistant lung cancer"
author:
  - name: Aurélie Pinchart
date: 10-11-2019
categories:
  - track
preview: 
output:
  distill::distill_article:
    self_contained: false
---

@@

Source of the article: <WWW.SCIENCEDAILY.COM/RELEASES/2019/09/190923170717.HTM>.

@@

|                             |                                                                                                                                                                                                                                                                                                                                                                           |
| --------------------------- | ------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------- |
| Researchers                 | Medical College of Georgia at Augusta University (lead authors : Dr. Wei Xiao, Dr. Mumtaz Rojiani, Dr. Amyn Rojiani)                                                                                                                                                                                                                                                      |
| Published in                | ScienceDaily, 23 September 2019                                                                                                                                                                                                                                                                                                                                           |
| General topic               | The way cancerous cells avoid apoptosis (non-small cell lung cancer)                                                                                                                                                                                                                                                                                                      |
| Procedure/what was examined | goal was to evidence link between TIMP-1 and resistance to chemotherapy + they used two drugs to destroy TIMP-1, then also destroy it by antibodies + added TIMP-1 to see the effect, then added IL-6  + STAT3 : regulator of gene activity (cell growth,division,  movement, apoptosis)                                                                                  |
| Conclusions/discovery       | high rate of TIMP-1 increases rate of IL-6 which make cells avoid apoptosis + low rate of TIMP-1 => lower rate of IL-6 => more apoptosis of cancerous cells => higher survival rate for patients + adding IL-6 has no real effect on apoptosis + remaining cancerous cells are more resistant + high level of IL-6 => STAT3 moves to nucleus => helps to reduce apoptosis |
| Remaining questions         | Does STAT3 activate more TIMP-1 production ?                                                                                                                                                                                                                                                                                                                              |
